Paper Nine Summary

### 2015-11-30 hw/read/9/summary.tex
Added some features for reading 9

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{babel}
\begin{document}
\title{Paper Nine Summary}

@@

\section*{Feature Extraction}

>>>>

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{babel}
\usepackage{hyperref} 
\begin{document}
\title{Paper Nine Summary}

@@

\section*{Feature Extraction}
\begin{description}
\item[{Motivational statements}] Cross-project defect prediction is often necessary for new projects, but doesn't always yield good results. Therefore, the authors hope to employ transfer defect learning to improve the performance of these models.
\item[{Data}] The authors have provided the data used in their experiments at\\
 \href{https://sites.google.com/site/transferdefect/}{https://sites.google.com/site/transferdefect/}.
\item[{Future work}] The authors were looking into transferring knowledge across entire domains as an extension of transfer learning. They were also interested in seeing which other prediction and recommendation systems might benefit from transfer learning.
\end{description}
